### 2015-05-13 evaluation.tex
update

Using the race freedom guarantees that \whoop provides, we managed to significantly accelerate \corral in most of our benchmarks; the best performance was achieved using the \yieldmr instrumentation (see Table~\ref{tab:results}). Figure~\ref{fig:plot} shows that most of our speedups using \yieldmr are in the range of 1.5--10$\times$; whereas in ssu100, and pc8736x\_gpio respectively, we achieved a speedup greater than 10$\times$, and 20$\times$ respectively, using a csb of 9. We notice that a higher csb can potentially result into greater speedups, when exploiting \whoop. This is expected, as a higher csb directly translates into a larger sequentialized program, and thus \whoop has more opportunities to reduce the sequentialization.

However, if \whoop fails to verify any race-related properties of a driver, it might actually slow down \corral. This can be noticed in the sx8 driver, where \whoop does not verify any pairs, causing unnecessary overhead. Even if \whoop verified 46 out of 47 memory regions, it still fails to speedup \corral using \yieldmr. This is probably because \corral manages to verify the only 2 pairs of sx8 quite fast (21.4 seconds with csb of 9), and thus the overhead of using \whoop overwhelms any benefits from our fine-grained instrumentation.

>>>>

Using the race-freedom guarantees from \whoop, we managed to significantly accelerate \corral in most of our benchmarks; the best results were achieved using \yieldmr. Figure~\ref{fig:plot} shows that most speedups using \yieldmr are in the range of 1.5--10$\times$; while in ssu100, and pc8736x\_gpio respectively, we achieved a speedup greater than 10$\times$, and 20$\times$ respectively, using a csb of 9. We notice that a higher csb typically results into greater speedups, when exploiting \whoop. This is expected, as a higher csb directly translates into a larger sequentialized program, and thus \whoop has more opportunities to reduce the sequentialization.

However, if \whoop fails to verify any race-related properties of a driver, it might actually slow down \corral. We noticed this in the sx8 driver, where \whoop does not verify any pairs, causing unnecessary overhead. Although \whoop verified 46 out of 47 memory regions, it still fails to speedup \corral using \yieldmr. This might be because \corral verifies the only 2 pairs of sx8 quite fast (21.4 seconds with csb of 9), and thus the overhead of using \whoop overwhelms any benefits from our fine-grained instrumentation.
